\documentclass[a4,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}

\usepackage[margin=0.75cm, top=0.75cm]{geometry}

% \pagestyle{fancy}
% \fancyhf{} 
% \fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\definecolor{UI_blue}{RGB}{35, 74, 82}


\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]




\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting - tighter spacing than itemize
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}


%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

\newcommand{\hrole}[2]{{\fontsize{11}{12}\selectfont \textbf{\underline{#1}}  \hfill{#2}}}

\newcommand{\hprojectname}[1]{\vspace{0.4cm}\noindent\textbf{#1}\vspace{-0.1cm}}


%%%% Set Subsection formatting
\titleformat{\subsection}{\vspace{0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]

\begin{document}


\begin{center}
    \begin{minipage}[b]{0.65\textwidth}
            \raggedright
            {\fontsize{32}{38}\selectfont Tushar Pawar} \\ %
            \vspace{0.2cm}
            {\color{UI_blue} \Large{Senior Software Engineer, Machine Learning}} \\
    \end{minipage}%
    \begin{minipage}[b]{0.35\textwidth}
            \flushright \large
            +91-9833588079 \\
            \href{mailto:tusharvijaypawar@gmail.com}{tusharvijaypawar@gmail.com} \\
            {\href{https://www.linkedin.com/in/backalla/}{linkedin.com/in/backalla} }
    \end{minipage}

\vspace{-0.15cm}
{\color{UI_blue} \hrulefill}
\end{center}

\noindent\textit{\textbf{Summary}}: Summary
\section{Experience}
\subsection{\hrole{Senior Software Engineer - Google - AI Research Accelerator Team}{Oct 2023 --- Present}}

    \hprojectname{Gemini Nano v4 Post-train Evals}
    \begin{zitemize}
        \item Built a synthetic data generation pipeline using \textbf{Gemini 2.5 Pro} to produce human-reviewed post-training datasets across 7 languages for \textbf{Gemini Nano v4}, covering translation, summarization, chat, and proofreading capabilities.
        \item Developed \textbf{LLM-as-judge autoraters} evaluating model outputs on naturalness, verbosity, and language adherence, surfacing critical capability gaps in non-English languages.
        \item Created an end-to-end eval automation platform enabling DeepMind engineers to benchmark Nano v4 checkpoints against golden datasets with a leaderboard for tracking progress, significantly reducing model rollout effort.
    \end{zitemize}

    \hprojectname{LLM-Assisted Customer Support Agent}
    \begin{zitemize}
        \item Designed and built an end-to-end agentic support tool using Google's \textbf{ADK} framework with a multi-component pipeline: \textbf{RAG}-based knowledge retrieval for support documents and past cases, tool calling against internal Play Store APIs for account and metadata lookups, and a multi-LLM-agent chain for case summarization, response drafting, and guardrails to prevent data leaks.
        \item Implemented a \textbf{human-in-the-loop} feedback system where expert human support agents author golden responses and rate LLM outputs, enabling continuous quality monitoring and iterative model improvement.
        \item Achieved a \textbf{40\% reduction in case resolution time} and \textbf{autonomous resolution of 28\% of support cases} without human intervention, while sustaining high \textbf{CSAT scores} across Google Play developer support.
    \end{zitemize}

    \hprojectname{RCS Spam Protection}
    \begin{zitemize}
        \item Founding SWE on ML spam protection system for RCS Messaging \textbf{(1B+ users)}. Built spam detection ML system with the unique constraint of building models without access to E2E-encrypted message content. Designed the modeling strategy and launched an onboarding model that proactively flags spammers at registration time, \textbf{blocking 20k+ new spammer registrations per day} at \textbf{FPR $<$ 0.3\%}.
        \item Drove end-to-end data and infrastructure foundations on a greenfield project with no labels or north-star metric: built a distributed data aggregation pipeline, collaborated with User Safety Team to define ground truth spam markers, established go/no-go launch criteria, and owned model experimentation via automater retraining and metrics dashboards to support post-launch iteration.
        \item Built interpretability tools to inspect model behaviour and uncover blind spots and biases using \textbf{SHAP Analysis}. Also built explainability tools to debug model mistakes and detect data drift to trigger model retraining.
    \end{zitemize}
    
    \hprojectname{DMA Compliance - Technical Asset Recommendation}
    \begin{zitemize}
        \item ML lead for a Google-wide DMA compliance initiative requiring \textasciitilde800M technical assets (configs, data tables, binaries) to be mapped to \textasciitilde6k products to enforce strict cross-product data boundaries and prevent data leakage.
        \item Designed and built an ML system using a \textbf{two-tower recommender} to predict asset-product associations, auto-generating owner verification emails to fast-track the mapping campaign at scale.
        \item Built the full training and evaluation pipeline — leveraged verified asset-product mappings as positive signal and generated \textbf{hard negatives} to improve model discriminability; achieved high precision and recall on held-out evaluation sets.
        \item Completed full migration within \textbf{3 months}, meeting the compliance deadline and avoiding DMA regulatory risk for the company.
    \end{zitemize}
    
    

\subsection{\hrole{Machine Learning Engineer - Booking.com - ML Platform Team}{April 2022 --- Sept 2023}}

    \hprojectname{ML Inference Platform}
    \begin{zitemize}
        \item Owned the integration of \textbf{Tensorflow Serving} as a new inference backend for Booking.com's ML platform, replacing a legacy Java/Scala serving layer limited to older TF versions and LightGBM, enabling support for modern TF versions and new GBDT frameworks like \textbf{TFDF}. Each model type is hosted in an isolated Docker container exposing gRPC endpoints.
        \item New backend scaled to handle peak load of \textbf{170 Billion predictions per day} at \textbf{p99.9 latency of 50ms}.
    \end{zitemize}

    \hprojectname{Cloud Migration}
    \begin{zitemize}
        \item Led migration of ML serving deployments from unreliable on-prem infrastructure to \textbf{AWS}, collaborating with cross-functional infra and data storage teams. Migrated \textbf{\textasciitilde80\% of serving load} to AWS, significantly reducing dependency on on-prem infra.
    \end{zitemize}

    \hprojectname{Self-Serve Model Onboarding CLI}
    \begin{zitemize}
        \item Built a \textbf{CLI tool} enabling platform users to independently onboard and manage their ML models on the serving platform without platform team involvement, eliminating a critical bottleneck and significantly reducing support ticket volume.
    \end{zitemize}

\subsection{\hrole{Head of AI-Cloud Engineering - Infilect Technologies} {June 2020 --- March 2022}}

    \hprojectname{ML Deployment Pipeline}
    \begin{zitemize}
        \item End to end ownership of entire ML model deployment pipeline. Scaled ML pipelines containing detection, segmentation and classification blocks to handle peak load of \textasciitilde60k images per hour.
    \end{zitemize}

    \hprojectname{ML Development Platform}
    \begin{zitemize}
        \item Led the development of internal tools for designing, developing, testing and deploying ML models. Similar to \textbf{Tensorboard}.
    \end{zitemize}

    \hprojectname{Team \& Project Leadership}
    \begin{zitemize}
        \item Mentored junior team members and provided technical leadership in ML system design.
        \item Managed project priorities, deadlines, stakeholder alignment, and deliverables to ensure successful completion of high impact projects.
    \end{zitemize}

\subsection{\hrole{Machine Learning Engineer - Infilect Technologies}{Sept 2018 --- June 2020}}

    \hprojectname{ML Debug \& Visualization Interface}
    \begin{zitemize}
        \item Designed a custom debug interface built in \textbf{React} and \textbf{Django} backend which helped ML team to easily visualize model outputs, discover edge samples, fine-tune post-processing logic.
    \end{zitemize}

    \hprojectname{Model Training}
    \begin{zitemize}
        \item Trained object detectors, classifiers and segmentation models on internal training frameworks built using \textbf{PyTorch} and \textbf{Tensorflow}.
    \end{zitemize}

    \hprojectname{Image Search System}
    \begin{zitemize}
        \item Created image search system to find samples for classification data from huge untagged corpus of 55M images. Used  \textbf{Elasticsearch} to store embeddings and KNN plugin to query for embedding matches.
    \end{zitemize}


\subsection{\hrole{Research Engineer - Praemineo Technologies}{June 2017 --- Aug 2018}}

    \hprojectname{Multilingual OCR System}
    \begin{zitemize}
        \item Built a Multilingual OCR system to extract text from a document with \textbf{\textasciitilde96\% accuracy} using a \textbf{CNN and LSTM} based model.
    \end{zitemize}

    \hprojectname{Indoor Geolocation System}
    \begin{zitemize}
        \item Built Android app for non-GPS geolocation system using WiFi signal triangulation. Worked with accuracy of \textasciitilde2 meters indoors.
    \end{zitemize}

\vspace{-0.1cm}

\section{Projects} 
\subsection*{CLI tool for model management, {\normalsize\normalfont ML Platform Team, Booking.com }} 
    \begin{zitemize}
        \item Led the development of a CLI tool written in \textbf{Scala} to manage deployed ML models.  
        \item Users can directly interact with their models without configuring client tools and making API calls.
    \end{zitemize}


\subsection*{Model Training Framework, {\normalsize\normalfont ML Team, Infilect}}
    \begin{zitemize}
        \item Built internal framework to train object detector based on \textbf{SSD} and \textbf{retinanet} architectures. 
        \item Plug-and-play interface to easily train, debug and visualize model predictions and performance metrics. 
        \item \textbf{Reduced model training and data engineering time by 50\%}. 
    \end{zitemize}



\subsection*{AI Controller, {\normalsize\normalfont MLOps Team, Infilect }}
    \begin{zitemize}
        \item Built an internal framework for automated deployment system for all ML models on a distributed cluster of GPU nodes. Integrated \textbf{Prometheus} for centralized monitoring of all (\textasciitilde600) models deployed across \textasciitilde120 GPU nodes. Visualized using \textbf{Grafana} dashboard.
        \item Implemented load prediction algorithm based on historical load data. \textbf{Predictive scaling policy gave \textasciitilde25\% savings on cloud cost. }
    \end{zitemize}



\subsection*{AI Assisted data tagging, {\normalsize\normalfont ML Team, Infilect }}
    \begin{zitemize}
        \item Built AI assisted tool to improve data tagging speed and quality for detection and classification tasks. Self supervised data tagging using \textbf{BYOL} and \textbf{SimCLRv2} gave \textasciitilde60\% accuracy on unseen and untagged data. 
        \item Implemented iterative feedback loop to retrain the classifier to give better suggestions to data tagging team. 
        \item Integrated hard negative mining which improved downstream model performance by suggesting tough samples to human taggers.
    \end{zitemize}


\subsection*{Synthetic image data generator using Blender, {\normalsize\normalfont ML Team, Infilect }} 
    \begin{zitemize}
        \item Led the development of automated synthetic image data generation tool for detection and classification tasks using \textbf{Blender}. 
        \item Randomised scene generation with precise control over camera angles, lighting, objects configuration, texture and lens artefacts.
        \item Reduced the dependency on tagged data and gave \textbf{\textasciitilde15\% accuracy improvement} over model trained only on natural tagged data.
    \end{zitemize}

\section{Skills}
\begin{tabular}{p{12em} p{48em}}
\hskills{Programming Languages} &  Scala, Java, C, C++, Python, JavaScript, Shell  \\
\hskills{ML Development} & Tensorflow, PyTorch, LightGBM, NVIDIA Triton, TensorRT, ONNX, OpenCV, Numpy  \\
\hskills{Web Development} & React, Django, Flask, Node.js, MongoDB, PostgreSQL, Firebase \\
\hskills{Cloud Management} & Kubernetes, Ansible, Docker, Helm, Prometheus, Grafana, gcloud and boto SDK  \\
\hskills{Other tools} & Git, Postman, Streamlit, K9S, Linux CLI tools, Blender   \\
\end{tabular}
\vspace{-0.2cm}


\vspace{-0.2cm}

\end{document}